Embedded Meta-Learning: Toward more flexible deep-learning models

### 2019-05-15 writing/embedded_meta_learning.tex
Work work work

\section{Introduction}
Humans are able to use and reuse knowledge more flexibly than most deep learning models can \citep[e.g.][]{Lake2016, Marcus2018}. One fundamental reason for this is that humans are aware of what we are trying to compute and why. By contrast, there is a fundamental separation of knowledge within most deep neural networks -- although deep networks represent knowledge about data (in their activations) and knowledge about the structure of tasks (in their parameters), they do not represent any relationships between data and tasks. That is, a neural network's knowledge about what is being computed is only implicitly accessible to those computations. \par
There are a number of advantages to representing knowledge about data and tasks together. In particular, it can grant the ability to rapidly adapt behavior to a new task. The problem of rapid learning has been partially addressed by meta-learning systems \citep[e.g.][]{Vinyals2016, Finn2017a}. However, humans can use our knowledge of a task flexibly alter our behavior in accordance with a change in task demands or a single instruction. For example, once we learn to play a game, we can immediately switch to playing in order to lose, and can achieve reasonable performance without any retraining (i.e. zero-shot). Deep learning systems at present generally lack this representational flexibility. \par
In this paper, we propose a new class of tasks based on this idea: meta-mappings, i.e. mappings between tasks (see below). This type of transfer is easily accessible to humans \citep{Lake2016}, but is generally inaccessible to most deep-learning models. To address this challenge, we propose a new class of architectures which essentially take a functional perspective on meta-learning, and exploit the idea of homoiconicity. (A homoiconic programming language is one in which programs in the language can be manipulated by programs in the language, just as data can.) By treating both data and task behaviors as functions, we can conceptually think of both data \emph{and} learned task behaviors as transformable. This yields the ability to not only learn to solve new tasks, but to learn how to transform these solutions in response to changing demands. We demonstrate that our arhitectures can flexibly remap their behavior to address the meta-mapping challenge. EML may also offer other benefits, such as a useful framework for continual learning. We suggest that approaches like EML will be key to building more intelligent and flexible deep learning systems. \par

@@

\section{Embedded Meta-Learning (EML) architecture}
To achieve this, we propose a new class of Embedded Meta-Learning (EML) architectures which consist of two parts: 
\vspace{-0.75em}
\begin{enumerate} \setlength \itemsep{0em}
\item An input/output system: domain specific encoders and decoders (vision, language, etc.) that map into a shared embedding space $Z$.
\item A meta-learning system which embeds tasks into the shared embedding space $Z$, and learns to map task embeddings to behavior.
\end{enumerate}
\vspace{-0.75em}
The utility of having a completely shared space $Z$ in which data, language, and tasks are represented is that it allows for arbitrary mappings between these distinct types of data. In addition to basic tasks, the system could in principle learn to map language to tasks (follow instructions) or tasks to language (explaining behavior), or tasks to tasks (changing behavior based on examples). This is a step closer to the flexible reasoning humans display. \par
Without training on these mappings, of course, the system will not be able to execute them well. However, if it is trained on a broad enough set of such mappings, it will be able to generalize to new instances drawn from the same data/task distribution, as we demonstrate below. For instances that fall outside its data distribution, or for optimal performance, it may require some retraining, however. This reflects the structure of human behavior -- we are able to learn rapidly when new knowledge is relatively consistent with our previous knowledge, but learning an entirely new paradigm (such as calculus for a new student) can be quite slow \citep[c.f.][]{Kumaran2016}. \par 
\begin{figure}
\centering
\begin{tikzpicture}[auto, scale=0.75]
\node [dashblock] at (0, 0) (rep) {\begin{tabular}{c}$\bm{Z}$: \textbf{Shared} \\ \textbf{representation}\end{tabular}};

@@

Specifically, we embed inputs, targets, and mappings into a shared representational space $Z$. Inputs are embedded by a deep network $\mathcal{I}: \text{input} \rightarrow Z$. Model outputs are decoded from the representational space by a deep network $\mathcal{O}: Z \rightarrow \text{output}$. Target outputs are encoded by a deep network $\mathcal{T}: \text{targets} \rightarrow Z$. Given this, the task of mapping inputs to outputs can be framed as trying to find a transformation of the representational space that takes the (embedded) inputs from the training set to embeddings that will decode to the target outputs. These transformations are performed by a system with the following components (see Fig. \ref{architecture_fig} for a schematic):  
\vspace{-0.75em}
\begin{itemize} \setlength\itemsep{0em}
\item $\mathcal{M}: \{(Z, Z), ...\} \rightarrow Z $ -- the meta network, which takes a set of (input embedding, target embedding) pairs and produces a function embedding. 
\item $\mathcal{H}: Z \rightarrow \text{parameters}$ -- the hyper network, which maps a function embedding to parameters. 
\item $F: Z \rightarrow Z$ -- the transformation, implemented by a deep network parameterized by $\mathcal{H}$.
\vspace{-0.75em}
A basic forward pass through the system would proceed as follows. First, a training dataset is encoded by $\mathcal{I}$ and $\mathcal{T}$. Some of these examples are fed to $\mathcal{M}$ to produce a function embedding (the remainder can be unlabeled during inference, or held-out to avoid memorization during training). This function embedding is mapped through $\mathcal{H}$ to parameterize $F$, and then $F$ is used to process the remaining examples, and $\mathcal{O}$ to map the resultant embeddings to outputs. This system can be trained end-to-end. See appendix \ref{app_model_details} for detailed architecture, operation, and hyper-parameters. \par 

@@

For example, if the $z_{old}$ is the system's embedding for trying to win at go, and $z_{meta}$ is the meta-task of switching to trying to lose a game, then $\hat{z}_{new}$ could be interpreted as the system's guess at a losing strategy for go. We could then evaluate performance by how well the system actually loses at go with the $\hat{z}_{new}$ strategy. \par
Similarly, we could map from language to a task embedding, and then ask how well the system performs at the task specified by language. The key feature of our architecture -- the fact that tasks, data, and language are all embedded in a shared space -- allows substantial flexibility within a unified framework.

@@

\begin{figure}
\centering
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\textwidth]{figures/poly/meta_results.png}
\caption{From examples of mapping.}
\label{poly_meta_map_results_examples}
\end{subfigure}%
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\textwidth]{figures/poly/language_meta_results.png}
\caption{From language input.}
\label{poly_meta_map_results_language}
\end{subfigure}
\caption{The system generalizes to apply learned meta-mappings to new tasks, and to apply unlearned meta-mappings from seeing examples or systematic language. The solid line indicates optimal performance; the dashed line indicates chance performance (an untrained model). The system is able to execute meta-mappings either from examples (\subref{cards_meta_map_results_examples}) or from language cues (\subref{cards_meta_map_results_language}). Error-bars are bootstrap 95\%-CIs.} 
\label{poly_meta_map_results}
\end{figure}
As a proof of concept, we first evaluated the system on the task of learning polynomials of degree $\leq 2$ in 4 variables (i.e. the task was to regress functions of the form $p: \mathbb{R}^4 \rightarrow \mathbb{R}$ where $p \in \mathcal{P}_2 \left(\mathbb{R}\right)$, though the model was given no prior inductive bias toward polynomial forms). This yields an infinite family of base-level tasks (the vector space of all such polynomials), as well as many families of meta-mappings over tasks (for example, multiplying polynomials by a constant, squaring them, or permuting their input variables). This allows us to not only examine the ability of the system to learn to learn polynomials from data, but also to adapt its learned representations in accordance with these meta-tasks. Details of architecture and training can be found in appendix \ref{app_detailed_methods}.\par

@@

Our next case study was in the setting of simple card games, where the agent receives a hand and has to decide on a bet. There is no action besides betting, and depending on the opponent's hand the agent either wins or loses the amount bet. If it wins, it is rewarded the value of the bet, if it loses, it loses that value (i.e. receives a negative reward). This doesn't require long term planning, but does incorporate some aspects of reinforcement learning, namely stochastic feedback on only the action chosen. We considered five games that are simplified analogs of various real card games, including poker and blackjack (see Appendix \ref{meth_data_cards} for details of the games). We also considered several binary options that could be applied to the games, including trying to lose instead of trying to win, or switching which suit was more valuable. These are challenging manipulations, for instance trying to lose requires completely inverting the learned $Q$-function for the task. \par
In order to adapt the EML architecture, we made a very simple change. Instead of providing the system with (input, target) tuples to embed, we provided it with (state, action, reward) tuples, and trained it via a DQN-like approach \citep{Mnih2015} to predict rewards for each bet in each state. (A full RL framework is not strictly necessary here because there is no temporal aspect to the tasks; however, we saw it as a useful proof of concept.) The hand is explicitly provided to the network for each example, but which game is being played is implicitly captured in the training examples, without any explicit cues. That is, the system must learn to play directly from seeing a set of (state, action, reward) tuples which implicitly capture the structure and stochasticity of the game. We also trained the system on meta-tasks, such as to identifying the various types of games and options, and to make meta-mappings, for example switching from trying to win a game to trying to lose. Details of architecture and training can be found in appendix \ref{app_detailed_methods}. \par
\textbf{Basic meta learning:} First, we show that the system is able to achieve the basic goal of learning a held-out task from a few examples in Fig. \ref{cards_basic_results}. We compare two different possible hold-out sets: 1) train on half the tasks at random, or 2) specifically hold out all the ``Losers'' variations of the ``straight flush'' game. In either of these cases, the meta-learning system achieves well above chance performance (0) at the held out tasks, although it is slightly worse at generalizing to the targeted hold out, despite having more training tasks in that case. It is worth noting that the sample complexity in terms of number of tasks trained on is not that high, even training on 20 randomly selected tasks leads to good generalization to the held-out tasks. Furthermore, the task embeddings generated by the system are organized by the features of the games, see appendix \ref{app_cards_tsne}. Finally, the system can integrate new tasks quite rapidly (fig. \ref{cards_basic_integration_results}).\par
\textbf{Meta mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings (mappings over tasks) in order to flexibly reconfigure its behavior. For example, if the system is trained to map games to their losers variations, it can generalize this mapping to a game it has not been trained to map, even if the source or target of that mapping is held out from training. In Fig. \ref{cards_meta_map_results}) we demonstrate this by taking the mapped embedding and evaluating the reward received by playing the targeted game with it. This task is more difficult than simply learning to play a held out game from examples, because the system will actually receive no examples of the target game (when it is held out). Furthermore, in the case of the losers mapping, leaving the strategy unchanged would produce a large negative reward, and chance performance would produce 0 reward, so it is encouraging to see rewards that are substantially above 0. Again, given a small amount of additional training on the new games, the system can learn how to achieve this mapping perfectly. \par

@@

%\textbf{Basic language (language $\rightarrow$ task):} Next, we show that the system is able to perform a held-out task based on a linguistic description alone. The system is significantly better than chance at this task, as shown in Fig. \ref{cards_language_basic_results}, but it is substantially less successful at this task than at learning from examples. This is perhaps unsurprising, however, since examples contain richer information about the structure of the task. (Note that the targeted 10\% was run using an older version of the code. Results may improve slightly when it is re-run, but based on the random 50\% hold-out results, the change doesn't make too substantial a difference.)\par
%Intriguingly, the system also shows more run-to-run variability in its generalization from language, especially with a targeted hold-out. This suggests that language learning in this context may be quite sensitive to initialization, possibily because of the poverty of the signal relative to the capacity of the network. Interestingly, simply applying dropout does not seem to ameliorate this. \par
%\begin{figure}[H]
%\begin{subfigure}[t]{0.5\textwidth}
%\centering
%\includegraphics[width=\textwidth]{figures/language_basic.png}
%\caption{Average rewards}
%\end{subfigure}%
%\begin{subfigure}[t]{0.5\textwidth}
%\includegraphics[width=\textwidth]{figures/language_basic_by_run.png}
%\caption{Density plot of rewards received on different held-out tasks on different runs of the model.}
%\end{subfigure}
%\caption{The system generalizes to held out tasks based on language alone. However, it is substantially less good at this task than generalizing to a held-out task based on examples. Furthermore, it shows more run-to-run variability and within-run variability.}
%\label{cards_language_basic_results}
%\end{figure}
%\newpage
%\textbf{Meta language (language $\rightarrow (\text{task} \rightarrow \text{task})$):} Finally, in Fig, \ref{cards_language_meta_results}, we show that the system is able to perform meta-mappings from language comparably to how it performs them from examples. Note that this is in some ways an easier task than the basic language-mapping task. \par
%\begin{figure}[H]
%\centering
%\includegraphics[width=0.66\textwidth]{figures/language_meta_mapping.png}
%\caption{The system generalizes to meta-mapping new tasks based on language. It performs this comparably to meta-mapping based on examples of mappings.}
%\label{cards_language_meta_results}
%\end{figure}

@@

There has also been other recent interest in task (or function) embeddings. In simultaneous work Achille et al. \citep{Achille2019} proposed computing embeddings for tasks from the Fisher information of the parameters in a model tuned (final layer only) on the task. They show that this captures some interesting properties of the tasks, including some types of semantic relationships, and can help identify models that can perform well on a task. Rusu and colleagues recently suggested a similar meta-learning framework where latent codes are computed for a task which can be decoded to a distribution over parameters \citep{Rusu2019}. Other recent work has tried to learn representations for skills \citep[e.g.][]{Eysenbach2019} or tasks \citep[e.g.]{Hsu2019} for exploration and representation learning. Our perspective can be seen as a generalization of these that learns task embeddings in an end-to-end way, allows parameterizing a model (while some approaches only allow selection), but most importantly allows for remapping of behavior by meta-tasks. To the best of our knowledge none of the prior work has explored meta-mappings. \par

@@

We think that the general perspective of embedding tasks and considering meta-mappings will yield many fruitful future directions. We hope that our work will inspire more exploration of behavior adaptation, especially in tasks beyond the simple domains we considered here. To this end, we suggest the creation of meta-learning datasets which include information not only about tasks, but about the relationships between them. For example, as we alluded to above, tasks such as visual question-answering \citep[e.g.][]{Antol2015} can be usefully interpreted from this perspective (a question essentially yields a function from images to answers, and there are many systematic relationships between these functions), as can reinforcement learning tasks which involve executing instructions \citep[e.g.][]{Hermann2017, Co-Reyes2019}. Furthermore, we think our work provides a novel perspective on the types of flexibility that human intelligence exhibits, and thus hope that it may have implications for cognitive science. \par 

@@

@@

\subsection{Source repositories}
The full code for the simulations and analyses can be found on github:
\begin{itemize}
\item \url{https://github.com/lampinen/polynomials}
    \begin{itemize}
        \item See the \verb|continual_learning| and \verb|language_meta_only| branches for the continual learning and language results, respectively. 
    \end{itemize}
\item \url{https://github.com/lampinen/meta_cards} 
\end{itemize}
%%(will be made available in the de-anonymized version.)
\section{Card game $t$-SNE} \label{app_cards_tsne}
We performed $t$-SNE \citep{LaurensvanderMaaten2008} on the task embeddings of the system at the end of learning the card game tasks, to evaluate the organization of knowledge in the network. In fig. \ref{fig_cards_tsne_basic} we show these embeddings for just the basic tasks. The embeddings show systematic grouping by game attributes. In fig. \ref{fig_cards_tsne_full} we show the embeddings of the meta and basic tasks, showing the organization of the meta-tasks by type. \par 
\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{figures/basic_tsne_basic_final.png}
\caption{$t$-SNE embedding of the function embeddings the system learned for the basic card game tasks. (Note that the pairs of nearby embeddings differ in the ``suits rule`` attribute, discussed in appendix \ref{meth_data_cards}.)} 
\label{fig_cards_tsne_basic}
\end{figure}%
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{figures/basic_tsne_full_final.png}
\caption{$t$-SNE embedding of the function embeddings the system learned for the meta tasks (basic tasks are included in the background).} 
\label{fig_cards_tsne_full}
\end{figure}

>>>>

\section{Introduction}
Humans are able to use and reuse knowledge more flexibly than most deep learning models can \citep[e.g.][]{Lake2016, Marcus2018}. One fundamental reason for this is that humans are aware of what we are trying to compute and why. By contrast, there is a fundamental separation of knowledge within most deep neural networks -- although deep networks represent knowledge about data (in their activations) and knowledge about the structure of tasks (in their parameters), they do not represent any relationships between data and tasks. That is, a neural network's knowledge about what is being computed is only implicitly accessible to those computations. \par
There are a number of advantages to representing knowledge about data and tasks together. In particular, it can grant the ability to rapidly adapt behavior to a new task. The problem of rapid learning has been partially addressed by meta-learning systems \citep[e.g.][]{Vinyals2016, Finn2017a}. However, humans can use our knowledge of a task to flexibly alter our behavior in accordance with a change in task demands or a single instruction. For example, once we learn to play a game, we can immediately switch to playing in order to lose, and can achieve reasonable performance without any retraining (i.e. zero-shot). Deep learning systems at present generally lack this representational flexibility. \par
In this paper, we propose a new class of tasks based on this idea: meta-mappings, i.e. mappings between tasks (see below). This type of transfer is easily accessible to humans \citep{Lake2016}, but is generally inaccessible to most deep-learning models. To address this challenge, we propose a new class of architectures which essentially take a functional perspective on meta-learning, and exploit the idea of homoiconicity. (A homoiconic programming language is one in which programs in the language can be manipulated by programs in the language, just as data can.) By treating both data and task behaviors as functions, we can conceptually think of both data \emph{and} learned task behaviors as transformable. This yields the ability to not only learn to solve new tasks, but to learn how to transform these solutions in response to changing demands. We demonstrate that our architectures can flexibly remap their behavior to address the meta-mapping challenge. EML may also offer other benefits, such as a useful framework for continual learning. We suggest that approaches like EML will be key to building more intelligent and flexible deep learning systems. \par

@@

\section{Embedded Meta-Learning (EML) architecture}
EML architectures consist of two parts: 
\vspace{-0.75em}
\begin{enumerate} \setlength \itemsep{0em}
\item An input/output system: domain specific encoders and decoders (vision, language, etc.) that map into a shared embedding space $Z$.
\item A meta-learning system which embeds tasks into the shared embedding space $Z$, and learns to map task embeddings to behavior.
\end{enumerate}
\vspace{-0.75em}
The utility of having a completely shared space $Z$ in which data, language, and tasks are represented is that it allows for arbitrary mappings between these distinct types of data. In addition to basic tasks, the system could in principle learn to map language to tasks (follow instructions) or tasks to language (explaining behavior), or tasks to tasks (changing behavior based on examples). This is a step closer to the flexible reasoning humans display. \par
Without training on these mappings, of course, the system will not be able to execute them well. However, if it is trained on a broad enough set of such mappings, it will be able to generalize to new instances drawn from the same data/task distribution, as we demonstrate below. For instances that fall outside its data distribution, or for optimal performance, it may require some retraining, however. This reflects the structure of human behavior -- we are able to learn rapidly when new knowledge is relatively consistent with our previous knowledge, but learning an entirely new paradigm (such as calculus for a new student) can be quite slow \citep[c.f.][]{Kumaran2016}. \par 
\begin{figure}
\centering
\begin{tikzpicture}[auto, scale=0.75]
\node [dashblock] at (0, 0) (rep) {\begin{tabular}{c}$\bm{Z}$: \textbf{Shared} \\ \textbf{representation}\end{tabular}};

@@

Specifically, we embed inputs, targets, and mappings into a shared representational space $Z$. Inputs are embedded by a deep network $\mathcal{I}: \text{input} \rightarrow Z$. Model outputs are decoded from the representational space by a deep network $\mathcal{O}: Z \rightarrow \text{output}$. Target outputs are encoded by a deep network $\mathcal{T}: \text{targets} \rightarrow Z$.\par
Given this, the task of mapping inputs to outputs can be framed as trying to find a transformation of the representational space that takes the (embedded) inputs from the training set to embeddings that will decode to the target outputs. These transformations are performed by a system with the following components (see Fig. \ref{architecture_fig} for a schematic): $\mathcal{M}: \{(Z, Z), ...\} \rightarrow Z $ -- the meta network, which takes a set of (input embedding, target embedding) pairs and produces a function embedding. $\mathcal{H}: Z \rightarrow \text{parameters}$ -- the hyper network, which maps a function embedding to parameters. $F: Z \rightarrow Z$ -- the transformation, implemented by a deep network parameterized by $\mathcal{H}$. \par
A basic forward pass through the system would proceed as follows. First, a training dataset is encoded by $\mathcal{I}$ and $\mathcal{T}$. These examples are fed to $\mathcal{M}$ to produce a function embedding. This function embedding is mapped through $\mathcal{H}$ to parameterize $F$, and then $F$ is used to process a second dataset, and $\mathcal{O}$ to map the resultant embeddings to outputs. This system can be trained end-to-end on targets for the second dataset. See appendix \ref{app_model_details} for detailed architecture, operation, and hyper-parameters. \par 

@@

For example, if the $z_{old}$ is the system's embedding for trying to win at go, and $z_{meta}$ is the meta-task of switching to trying to lose a game, then $\hat{z}_{new}$ could be interpreted as the system's guess at a losing strategy for go. We could then evaluate how well the system actually loses with the $\hat{z}_{new}$ strategy. \par
Similarly, we could map from language to a task embedding, and then evaluate the system at the specified task. The key feature of our architecture -- the fact that tasks, data, and language are all embedded in a shared space -- allows substantial flexibility within a unified framework.

@@

\begin{figure}
\centering
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\textwidth]{figures/poly/meta_results.png}
\caption{From examples of mapping.}
\label{poly_meta_map_results_examples}
\end{subfigure}%
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\textwidth]{figures/poly/language_meta_results.png}
\caption{From language input.}
\label{poly_meta_map_results_language}
\end{subfigure}
\caption{The system generalizes to apply learned meta-mappings to new tasks, and to apply unlearned meta-mappings from seeing examples or systematic language. The solid line indicates optimal performance; the dashed line indicates chance performance (an untrained model). The system is able to execute meta-mappings either from examples (\subref{cards_meta_map_results_examples}) or from language cues (\subref{cards_meta_map_results_language}). Error-bars are bootstrap 95\%-CIs.} 
\label{poly_meta_map_results}
\end{figure}
As a proof of concept, we first evaluated the system on the task of learning polynomials of degree $\leq 2$ in 4 variables (i.e. the task was to regress functions of the form $p: \mathbb{R}^4 \rightarrow \mathbb{R}$ where $p \in \mathcal{P}_2 \left(\mathbb{R}\right)$, though the model was given no prior inductive bias toward polynomial forms). This yields an infinite family of base-level tasks (the vector space of all such polynomials), as well as many families of meta-mappings over tasks (for example, multiplying polynomials by a constant, squaring them, or permuting their input variables). This allows us to not only examine the ability of the system to learn to learn polynomials from data, but also to adapt its learned representations in accordance with these meta-tasks. Details of the architecture and training can be found in appendix \ref{app_detailed_methods}.\par

@@

Our next case study was in the setting of simple card games, where the agent receives a hand and has to decide on a bet. There is no action besides betting, and depending on the opponent's hand the agent either wins or loses the amount bet. This doesn't require long term planning, but does incorporate some aspects of reinforcement learning, namely stochastic feedback on only the action chosen. We considered five games that are simplified analogs of various real card games (see Appendix \ref{meth_data_cards}). We also considered several binary options that could be applied to the games, including trying to lose instead of trying to win, or switching which suit was more valuable. These are challenging manipulations, for instance trying to lose requires completely inverting a learned $Q$-function. \par
In order to adapt the EML architecture, we made a very simple change. Instead of providing the system with (input, target) tuples to embed, we provided it with (state, action, reward) tuples, and trained it via a DQN-like approach \citep{Mnih2015} to predict rewards for each bet in each state. (A full RL framework is not strictly necessary here because there is no temporal aspect to the tasks; however, we saw it as a useful proof of concept.) The hand is explicitly provided to the network for each example, but which game is being played is implicitly captured in the training examples, without any explicit cues. That is, the system must learn to play directly from seeing a set of (state, action, reward) tuples which implicitly capture the structure and stochasticity of the game. We also trained the system on meta-tasks, such as to identifying the various types of games and options, and to make meta-mappings, for example switching from trying to win a game to trying to lose. Details of the architecture and training can be found in appendix \ref{app_detailed_methods}. \par
\textbf{Basic meta learning:} First, we show that the system is able to achieve the basic goal of playing a held-out game from examples in Fig. \ref{cards_basic_results}. We compare two different possible hold-out sets: 1) train on half the tasks at random, or 2) specifically hold out all the ``losers'' variations of the ``straight flush'' game. In either of these cases, the meta-learning system achieves well above chance performance (0) at the held out tasks, although it is slightly worse at generalizing to the targeted hold out, despite having more training tasks in that case. Note that the sample complexity in terms of number of trained tasks is not that high, even training on 20 randomly selected tasks leads to good generalization to the held-out tasks. Furthermore, the task embeddings generated by the system are organized by the features of the games, see appendix \ref{app_cards_tsne}. Finally, the system can integrate new tasks rapidly (fig. \ref{cards_basic_integration_results}).\par
\textbf{Meta mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings (mappings over tasks) in order to flexibly reconfigure its behavior. For example, if the system is trained to map games to their losers variations, it can generalize this mapping to a game it has not been trained to map, even if the source or target of that mapping is held out from training. In Fig. \ref{cards_meta_map_results}) we demonstrate this by taking the mapped embedding and evaluating the reward received by playing the targeted game with it. This task is more difficult than simply learning to play a held out game from examples, because the system will actually receive no examples of the target game (when it is held out). Furthermore, in the case of the losers mapping, leaving the strategy unchanged would produce a large negative reward, and chance performance would produce 0 reward, so the results are quite good. \par

@@

@@

There has also been other recent interest in task (or function) embeddings. In simultaneous work Achille et al. \citep{Achille2019} proposed computing embeddings for visual tasks from the Fisher information of the parameters in a model partly tuned on the task. They show that this captures some interesting properties of the tasks, including some types of semantic relationships, and can help identify models that can perform well on a task. Rusu and colleagues recently suggested a similar meta-learning framework where latent codes are computed for a task which can be decoded to a distribution over parameters \citep{Rusu2019}. Other recent work has tried to learn representations for skills \citep[e.g.][]{Eysenbach2019} or tasks \citep[e.g.]{Hsu2019} for exploration and representation learning. Our perspective can be seen as a generalization of these that learns task embeddings in an end-to-end way, allows parameterizing a model (while some approaches only allow selection), but most importantly allows for remapping of behavior by meta-tasks. To the best of our knowledge none of the prior work has explored meta-mappings. \par

@@

We think that the general perspective of embedding tasks and considering meta-mappings will yield many fruitful future directions. We hope that our work will inspire more exploration of behavioral adaptation in areas beyond the simple domains we considered here. To this end, we suggest the creation of meta-learning datasets which include information not only about tasks, but about the relationships between them. For example, as we alluded to above, tasks such as visual question-answering \citep[e.g.][]{Antol2015} can be usefully interpreted from this perspective (a question essentially yields a function from images to answers, and there are many systematic relationships between these functions), as can reinforcement learning tasks which involve executing instructions \citep[e.g.][]{Hermann2017, Co-Reyes2019}. Furthermore, we think our work provides a novel perspective on the types of flexibility that human intelligence exhibits, and thus hope that it may have implications for cognitive science. \par 

@@

Num. runs & 5 & 5 & 10 \\ \hline

@@

\subsection{Source repositories}
The full code for the experiments and analyses can be found on github:
\begin{itemize}
\item \url{https://github.com/lampinen/polynomials}
    \begin{itemize}
        \item See the \verb|continual_learning| and \verb|language_meta_only| branches for the continual learning and language results, respectively. 
    \end{itemize}
\item \url{https://github.com/lampinen/meta_cards} 
\end{itemize}
%%(will be made available in the de-anonymized version.)
\section{Card game $t$-SNE} \label{app_cards_tsne}
We performed $t$-SNE \citep{LaurensvanderMaaten2008} on the task embeddings of the system at the end of learning the card game tasks, to evaluate the organization of knowledge in the network. In fig. \ref{fig_cards_tsne_basic} we show these embeddings for just the basic tasks. The embeddings show systematic grouping by game attributes. In fig. \ref{fig_cards_tsne_full} we show the embeddings of the meta and basic tasks, showing the organization of the meta-tasks by type. \par 
\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{figures/basic_tsne_basic_final.png}
\caption{$t$-SNE embedding of the function embeddings the system learned for the basic card game tasks. (Note that the pairs of nearby embeddings differ in the ``suits rule`` attribute, discussed in appendix \ref{meth_data_cards}.)} 
\label{fig_cards_tsne_basic}
\end{figure}%
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{figures/basic_tsne_full_final.png}
\caption{$t$-SNE embedding of the function embeddings the system learned for the meta tasks (basic tasks are included in the background).} 
\label{fig_cards_tsne_full}
\end{figure}
